The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/accuracy.tex
Reworked accuracy section.

Now comes the time to justify our efforts by comparing the accuracy of our
skew-normal approximation to that of the normal. Naturally, we are primarily
interested in cases where the normal approximation performs poorly, that is
binomials where $n$ is small and $p$ is either close to 0 or 1.\footnotemark

@@

At very small $n$ and $p$, our skew-normal curve follows the shape of the
binomial much more closely than the normal. However, as $n$ grows, the Central
Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
as we would expect, the skew-normal method is most valuable at small $n$ and
extreme $p$.

@@

Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
\ref{app:figures} shows the MABS of the skew-normal and normal approximations
as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
the normal considerably in the extreme ranges, with the two approximations
converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.

>>>>

Now comes the time to justify our efforts by comparing the accuracy of our
skew-normal approximation to that of the normal.

We are naturally most interested in cases where other solutions perform poorly.
Recall that when $n$ is small, it is feasible to calculate the binomial
directly, and when $n$ is large or $p$ is close to 0.5, the normal distribution
provides an adequate approximation. Therefore, our interest is primarily in
cases where $n$ is moderate and $p$ is extreme (close to 0 or 1).\footnotemark

@@

The graphs show that at moderate $n$ and small $p$, our skew-normal curve
follows the shape of the binomial much more closely than the normal. As $n$
grows, however, the Central Limit Theorem begins to exert its effect and the
normal distribution "catches up" in accuracy. Thus as we would expect, the
skew-normal approximation is of greatest value in the former set of cases.

@@

Figure \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
\ref{app:figures} shows the MABS of the skew-normal and normal approximations
as a function of $p$ and $n$, respectively.

In figure \ref{fig:mabs-fixed-n}, the MABS of the normal approximation is more
than four times that of the skew-normal when $p$ is very close to 0. The two
error curves converge and eventually meet as $p$ approaches 0.5 and the
binomial becomes symmetrical.

Similarly, in figure \ref{fig:mabs-fixed-p}, the normal MABS is roughly six
times the skew-normal MABS. Interesting, the error curves converge much more
slowly this time, leading to the pleasant (if surprising) conclusion that when
$p$ is extreme, the skew-normal gains us a measure of accuracy even at very
large $n$.
